Parallelization of Fast $\ell_1$-Minimization for Face Recognition

### 2011-05-29 main.tex
unified todo list
Added recognition stage runtime plot, fixed legend

The following experiment fulfills the dual purpose of verifying the accuracy of
the alignment stage, and motivating a threshold on how many users are kept for
the recognition stage.  Setting this threshold establishes a compromise between
recognition speed and potential recognition rate.  To explore the affect of the
threshold on potential recognition rate, we vary the number of users kept for
the recognition stage and estimate the probability of the test user being
among the set of training users kept for the recognition stage.  This curve
bounds above the achievable recognition rate of the overall pipeline.  As can
be seen in Figure \ref{fig:user_alignment_rank_plot}, there are rapidly
diminishing returns as the number of kept users is increased beyond 20; a small
fraction of the gallery.
\begin{figure} 
\centering
\includegraphics[width=3.4in]{figures/user_alignment_rank_plot}
\caption{Probability of the test user being kept for the recognition stage vs.
number of training users kept for the recognition stage.}
\label{fig:user_alignment_rank_plot} \end{figure}

@@

% To do list:
%Add experiment timing for one instance per core on cpu?
%Unify plot styles
%Interpret 2 percent accuracy difference
%Update speed comparisons and diagrams to GTX 580?
%Better citation for previously reported speed?
%Figure tweaks from Allen

>>>>

%The following experiment fulfills the dual purpose of verifying the accuracy of
%the alignment stage, and motivating a threshold on how many users are kept for
%the recognition stage.  Setting this threshold establishes a compromise between
%recognition speed and potential recognition rate.  To explore the affect of the
%threshold on potential recognition rate, we vary the number of users kept for
%the recognition stage and estimate the probability of the test user being
%among the set of training users kept for the recognition stage.  This curve
%bounds above the achievable recognition rate of the overall pipeline.  As can
%be seen in Figure \ref{fig:user_alignment_rank_plot}, there are rapidly
%diminishing returns as the number of kept users is increased beyond 20; a small
%fraction of the gallery.
%\begin{figure} 
%\centering
%\includegraphics[width=3.4in]{figures/user_alignment_rank_plot}
%\caption{Probability of the test user being kept for the recognition stage vs.
%number of training users kept for the recognition stage.}
%\label{fig:user_alignment_rank_plot} \end{figure}

\begin{figure} 
\centering
\includegraphics[width=3.4in]{figures/speedVsResolution}
\caption{Recognition stage runtime vs. size of training database.}
\label{fig:recognition_stage_runtime} \end{figure}

@@
